%%%
% CSSE lab template
% Written March 28, 2011 by Tim Ekl
%
% This template is part of a template system; you should be generating a lab
% using the newlab.sh file. Once you have generated the lab, feel free to
% remove this comment.
%
% This lab has five TODO items that need to be completed manually after
% generating the lab from template. Suggestions are provided with each TODO.
%
% For more info and examples of labs built from this template, see:
% http://github.com/CSSE376/Labs (note you must be a 376 TA to access)
%%%

\documentclass{article}

\newcommand{\labduedate}{at the end of Week 1}

\input{../common/header}

\pagestyle{fancy}
\headheight 24pt
\begin{document}

\chead{\textcolor{Gray}{CSSE491 -- Scalable Computing Lab Assignment}}
\headsep = 24pt

\begin{center}
{ \large
\textbf{Lab \labnumber: \longproductname} \\
\textbf{Getting Started}
}
\end{center}

\subsection*{Objective}
The goal of this lab is to introduce students to server-side webapp programming using a number of relatively new frameworks. By the end of the lab, students should be acquainted with Node.js, MongoDB (and its Node library Mongoose), and Express.

\subsection*{Lab format}
As an introductory assignment, this lab primarily guides the user through the installation of Node.js components and dependencies, then instructs students on construction of a basic HelloWorld app. The lab is primarily guided.

\subsection*{Required materials}
Students will need a laptop with an active Internet connection.

\subsection*{Grading rubric}
\begin{tabular}{p{5.5in} r}
Questions 1-3 are worth \textbf{5} points each. & $3 \times 5 = 15$ \\
Tasks 1-4 are worth \textbf{5} points each. & $4 \times 5 = 20$ \\
Tasks 5-7 are worth \textbf{10} points each. & $3 \times 10 = 30$ \\ \hline
& \textbf{65} points
\end{tabular}

\subsection*{Due date}
The lab is due \textcolor{red}{\textbf{\labduedate}}.

\input{../common/turnin}

\task{5}{Install Node.js}

\begin{minted}{bash}
sudo apt-get install build-essential
sudo apt-get install python-software-properties
sudo add-apt-repository ppa:chris-lea/node.js
sudo apt-get update
sudo apt-get install nodejs
\end{minted}

\textit{Note: without the first three commands, a very old version may be installed.}

\task{5}{Install MongoDB}

\begin{minted}{bash}
sudo apt-key adv --keyserver keyserver.ubuntu.com --recv 7F0CEB10
echo "deb http://downloads-distro.mongodb.org/repo/ubuntu-upstart dist 10gen" | sudo tee -a /etc/apt/sources.list
sudo apt-get update
sudo apt-get install mongodb-10gen
\end{minted}

\textit{Note: With just the package} \verb!mongodb!, \textit{an old version may be installed.}

\task{5}{Install NPM}

\begin{minted}{bash}
sudo apt-get install curl
curl http://npmjs.org/install.sh | sudo sh
\end{minted}

\question{5}{It is advised not to install npm as root. Why?}

\task{5}{Install Express and Mongoose}

\begin{minted}{bash}
sudo npm install express mongoose -g
\end{minted}

\question{5} It is advised to install Express globally, since it has a common executable. However, Mongoose should not be installed globally. Why?

\task{10}{Hello, World}

\begin{minted}{bash}
express HelloWorld
cd HelloWorld && npm install
npm install mongoose
echo node_modules > .gitignore
\end{minted}

\question{5} Why do you think we need to install Mongoose locally even though it is already installed globally?

\task{10}{Write Mongoose models}

\begin{enumerate*}
\item Import mongoose
\item Connect to the database
\item Create a status schema
\item Create a status model
\item Create a status instance, if none exist
\item Export the status model
\end{enumerate*}

In the file \verb!models.js!, type:

\begin{minted}{javascript}
/**
 * Module dependencies.
 */

var mongoose = require('mongoose');

mongoose.connect('mongodb://localhost/hello_world');

var StatusSchema = new mongoose.Schema({
    message: String
});

var Status = mongoose.model('Status', StatusSchema);

Status.count(function(err, c) {
    if (c == 0) {
        var status = new Status();
        status.message = 'Hello, World';
        status.save()
    }
});

exports.Status = Status;
\end{minted}

\task{10}{Write an initial route and view}

In the file \verb!routes/index.js!, import the Status model by adding the line:

\begin{minted}{javascript}
var Status = require('../models').Status;
\end{minted}

Replace the basic view rendering (the line beginning \verb!res.render!) with:

\begin{minted}{javascript}
Status.find(function(err, statuses) {
    res.render('index', { title: 'Express', statuses: statuses });
});
\end{minted}

In the file \verb!views/index.jade!, add:

\begin{minted}{jade}
h2 Statuses
each status in statuses
  p #{status.message}
\end{minted}

\subsection*{Run your app}

Run the app by typing at a shell:

\begin{minted}{bash}
node app.js
\end{minted}

Now access the URL \href{http://localhost:3000/}{http://localhost:3000}; you should see a status-list page.

\input{../common/turnin}

\subsection*{Revision History}
\begin{itemize*}
 \item April 12, 2012: Lab converted to LaTeX by Tim Ekl
 \item March 9, 2012: Lab written by Samad Jawaid
\end{itemize*}

\end{document}
