%%%
% CSSE lab template
% Written March 28, 2011 by Tim Ekl
%
% This template is part of a template system; you should be generating a lab
% using the newlab.sh file. Once you have generated the lab, feel free to
% remove this comment.
%
% This lab has five TODO items that need to be completed manually after
% generating the lab from template. Suggestions are provided with each TODO.
%
% For more info and examples of labs built from this template, see:
% http://github.com/CSSE376/Labs (note you must be a 376 TA to access)
%%%

\documentclass{article}

\newcommand{\labduedate}{at the end of week 5}

\input{../common/header}

\pagestyle{fancy}
\headheight 24pt
\begin{document}

\chead{\textcolor{Gray}{CSSE491 -- Scalable Computing Lab Assignment}}
\headsep = 24pt

\begin{center}
{ \large
\textbf{Lab \labnumber: \longproductname} \\
\textbf{Tags}
}
\end{center}

\subsection*{Objective}
The objective of this lab is to expose students to one of the most important facets of scalable computing: search. By adding tags to photos stored in the HelloWorld app from Lab 4, this lab aims to explore search implementations in Node.js across large databases -- a key concept in scalable systems.

\subsection*{Lab format}
This lab, like most previous labs, is largely guided. However, it will require students to answer a number of comprehension questions, some of which may require independent research. There is also a small independent coding portion near the end of the lab.

\subsection*{Required materials}
Students will need:
\begin{itemize*}
\item The HelloWorld app from Lab 4
\item A laptop with an Internet connection
\item Photos from \href{http://interfacelift.com}{interfacelift} in \verb!public/img/interfacelift!
\end{itemize*}

\subsection*{Grading rubric}
\begin{tabular}{p{5.5in} r}
Tasks 1 and 3 are worth \textbf{5} points each & $2 \times 5 = 10$ \\
Task 2 is worth \textbf{10} points & $1 \times 10 = 10$ \\
Questions 1-3 are worth \textbf{5} points each & $3 \times 5 = 15$ \\ \hline
& \textbf{35} points
\end{tabular}

\subsection*{Due date}
The lab is due \textcolor{red}{\textbf{\labduedate}}.

\input{../common/turnin}

\task{5}{Update the Model}

Open the file \verb!models.js!, and make the following changes:

\begin{itemize*}
\item Add an attribute called \verb!tags! to the PhotoSchema definition of type String
\item In the function beginning \verb!Photo.count(function(...!, add the following:
\begin{itemize*}
\item A list of tags after the definition \verb!var FOLDER...!. This list should take the form:

\begin{minted}{javascript}
var TAGS = ['foo', 'bar', 'your', 'tags', 'here'];
\end{minted}

\item The following code block in the set of lines containing \verb!photo.path = ...!:

\begin{minted}{javascript}
var j = 0;
var n = Math.ceil(Math.random() * 5);
while (j < n) {
  var tag = TAGS[Math.round(Math.random() * (TAGS.length - 1))];
  if (photo.tags.indexOf(tag) == -1) {
    photo.tags.push(tag);
  }
  j++;
}
\end{minted}
\end{itemize*}
\end{itemize*}

\question{5} Explain, in your own words, what the new code block in the last bullet point above does.

\task{10}{Routing}

In the file \verb!app.js!, change:

\begin{minted}{javascript}
app.get('/photos/:page', routes.photos.all);
\end{minted}

to

\begin{minted}{javascript}
app.get('/photos/:page/:tag?', routes.photos.all);
\end{minted}

\question{5} We know that the colon indicates a route parameter; what do you think the question mark (e.g. \verb!:tag?!) indicates? Feel free to refer to Node.js or Express documentation.

Once the app is updated, edit the route it refers to. Open the file \verb!routes/photos.js! and make the following changes:

\begin{itemize}
\item Update \verb!exports.all = function(...! (after \verb!var page = ...;!) with:
\begin{minted}{javascript}
  var tag = req.params.tag;
  var query = {};
  if (tag) {
    query = {tags: {$in: [tag]}};
  }
\end{minted}

\item Update the same function (after \verb!if (page == 0) {...}!) with:

\begin{minted}{javascript}
  options.sort = {description: 1};
\end{minted}

\item Update the same function (after \verb!context.title = ...;!) with:

\begin{minted}{javascript}
    context.tag = tag;
    if (tag) {
      context.title += ' - ' + tag;
    }
\end{minted}

\item Finally, change
\begin{minted}{javascript}
Photo.find({}, ['path', 'description'], ...);
\end{minted}
to
\begin{minted}{javascript}
Photo.find(query, ['path', 'description', 'tags'], ...);
\end{minted}
\end{itemize}

\question{5} Describe, in your own words, what the updates listed above do.

\task{5}{Update the View}

So what's the desired user interface for tags? They should, at a minimum:

\begin{itemize*}
\item Be displayed below their respective photos
\item Link to result sets for the same tag
\end{itemize*}

To accomplish this, open \verb!views/photos.jade!. Add (after both \verb!href='/photos/' + (page + 1)! and \verb!href='/photos/' + (page - 1)!):

\begin{minted}{jade}
 + (tag && ('/' + tag) || '')
\end{minted}

Also, add (before \verb!div.alert.alert-info="..."!):

\begin{minted}{jade}
  div.btn-group
    each tag in center.tags
      a.btn(href='/photos/all/' + tag)=tag
  br
\end{minted}

\subsection*{Run the App}

Like always, test with:

\begin{itemize*}
\item \verb!node app.js!
\item \href{http://localhost:3000/photos}{http://localhost:3000/photos}
\end{itemize*}

\input{../common/turnin}

\subsection*{Revision History}
\begin{itemize*}
 \item Sat Apr 14 16:13:11 EDT 2012: Lab created with template generator
\end{itemize*}

\end{document}
