%%%
% CSSE lab template
% Written March 28, 2011 by Tim Ekl
%
% This template is part of a template system; you should be generating a lab
% using the newlab.sh file. Once you have generated the lab, feel free to
% remove this comment.
%
% This lab has five TODO items that need to be completed manually after
% generating the lab from template. Suggestions are provided with each TODO.
%
% For more info and examples of labs built from this template, see:
% http://github.com/CSSE376/Labs (note you must be a 376 TA to access)
%%%

\documentclass{article}

\newcommand{\labduedate}{at the end of Week 3}

\input{../common/header}

\pagestyle{fancy}
\headheight 24pt
\begin{document}

\chead{\textcolor{Gray}{CSSE491 -- Scalable Computing Lab Assignment}}
\headsep = 24pt

\begin{center}
{ \large
\textbf{Lab \labnumber: \longproductname} \\
\textbf{User Authentication}
}
\end{center}

\subsection*{Objective}
Up to this point, we've been writing a public webapp: anyone with the URL can view or modify data. However, security is a huge (and growing) concern online; this lab aims to introduce security concepts by integrating user authentication (via Twitter) with the existing HelloWorld app from labs 1 and 2.

\subsection*{Lab format}
As with previous labs, this lab is mostly guided. Students will get authentication tokens from Twitter, then modify existing app files to work against the Twitter user framework.

\subsection*{Required materials}
Students will need a laptop, an Internet connection, a Twitter account, and the HelloWorld app from labs 1 and 2.

\subsection*{Grading rubric}
\begin{tabular}{p{5.5in} r}
Question 1 is worth \textbf{5} points & $1 \times 5 = 5$ \\
Task 1 is worth \textbf{5} points & $1 \times 5 = 5$ \\
Tasks 2-4 are worth \textbf{10} points each & $3 \times 10 = 30$ \\ \hline
& \textbf{40} points
\end{tabular}

\subsection*{Due date}
The lab is due \textcolor{red}{\textbf{\labduedate}}.

\input{../common/turnin}

\task{5}{Twitter Keys}

Before we begin development, you'll need to fetch some authentication info from Twitter. If you haven't already, \href{http://twitter.com}{sign up} for a Twitter account. Then, at a shell in your HelloWorld directory, type:

\begin{minted}{bash}
$ sudo apt-get install nodejs-dev
$ npm install mongoose-auth
\end{minted}

You'll also need to alias the hostname \verb!local.host! to localhost; edit the file \verb!/etc/hosts! in your preferred text editor, and make sure it contains the line:

\begin{verbatim}
127.0.0.1 localhost local.host
\end{verbatim}

Now go to your \href{https://dev.twitter.com/apps}{Twitter app dev page} and add the following information:

\begin{center}
\begin{tabular}{p{1in} | p{4in}} \hline
\textbf{Access} & Read-only \\ \hline
\textbf{Callback URL} & \verb!http://local.host:3000/auth/twitter/callback! \\ \hline
\end{tabular}
\end{center}

Finally, create a new file called \verb!settings.js! in the root of your HelloWorld directory and add the following lines, replacing as appropriate:

\begin{minted}{javascript}
exports.SECRET_KEY = 'YOUR SECRET KEY';
exports.TWITTER_CONSUMER_KEY = 'YOUR CONSUMER KEY';
exports.TWITTER_CONSUMER_SECRET = 'YOUR CONSUMER SECRET';
\end{minted}

\task{10}{Modifying the App}

Open the file \verb!app.js!. Add near the top:

\begin{minted}{javascript}
var mongooseAuth = require('mongoose-auth');

var SECRET_KEY = require('./settings.js').SECRET_KEY;
\end{minted}

Now we need to remove some standard middleware and replace it with others. Comment the line:

\begin{minted}{javascript}
app.use(app.router);
\end{minted}

After this newly commented line, add:

\begin{minted}{javascript}
app.use(express.cookieParser());
app.use(express.session({secret: SECRET_KEY}));
app.use(mongooseAuth.middleware());
\end{minted}

Finally, add:

\begin{minted}{javascript}
mongooseAuth.helpExpress(app);
\end{minted}

\question{5} Why do you think we needed to remove the first middleware item (\verb!app.router!) before adding the others?

\task{10}{Updating the Models}

Our app file now supports authentication with the mongoose-auth package; however, we have yet to define what our user schema looks like in a way that our app can understand. Open the file \verb!models.js! and add the following block:

\begin{minted}{javascript}
var mongooseAuth = require('mongoose-auth');

var TWITTER_CONSUMER_KEY = require('./settings.js').TWITTER_CONSUMER_KEY;
var TWITTER_CONSUMER_SECRET = require('./settings.js').TWITTER_CONSUMER_SECRET;

var UserSchema = new mongoose.Schema();
UserSchema.plugin(mongooseAuth, {
    everymodule: {
        everyauth: {
            User: function() {
                return User;
            }   
        }   
    },  
    twitter: {
        everyauth: {
            myHostname: 'http://local.host:3000',
            consumerKey: TWITTER_CONSUMER_KEY,
            consumerSecret: TWITTER_CONSUMER_SECRET,
            redirectPath: '/' 
        }   
    }
});

var User = mongoose.model('User', UserSchema);
\end{minted}

\task{10}{Showing Login Status}

As with in lab 2, we've done everything on the backend to support a new feature, but where does it appear? We need to edit the view again. Open the file \verb!views/index.jade! and add:

\begin{minted}{jade}
h2 Authentication
- if(!everyauth.loggedIn)
  p
    a(href="/auth/twitter") Log in with Twitter
- else
  p #{everyauth.twitter.user.name}
  p #{everyauth.twitter.user.location}
  p
    a(href="http://www.twitter.com/" + everyauth.twitter.user.screen_name) @#{everyauth.twitter.user.screen_name}
  p
    a(href="/logout") Log out
\end{minted}

\subsection*{Try It Out}

As always, go to the URL \href{http://localhost:3000/}{http://localhost:3000} to try your new feature.

\input{../common/turnin}

\subsection*{Revision History}
\begin{itemize*}
\item April 13, 2012: Lab converted to LaTeX by Tim Ekl
\item March 13, 2012: Lab written by Samad Jawaid
\end{itemize*}

\end{document}
