%%%
% CSSE lab template
% Written March 28, 2011 by Tim Ekl
%
% This template is part of a template system; you should be generating a lab
% using the newlab.sh file. Once you have generated the lab, feel free to
% remove this comment.
%
% This lab has five TODO items that need to be completed manually after
% generating the lab from template. Suggestions are provided with each TODO.
%
% For more info and examples of labs built from this template, see:
% http://github.com/CSSE376/Labs (note you must be a 376 TA to access)
%%%

\documentclass{article}

\newcommand{\labduedate}{at the end of week 4}

\input{../common/header}

\pagestyle{fancy}
\headheight 24pt
\begin{document}

\chead{\textcolor{Gray}{CSSE491 -- Scalable Computing Lab Assignment}}
\headsep = 24pt

\begin{center}
{ \large
\textbf{Lab \labnumber: \longproductname} \\
\textbf{Photos}
}
\end{center}

\subsection*{Objective}
This lab continues to build on the HelloWorld example from previous labs, and is meant to demonstrate how Node.js apps can provide ``real-world'' functionality to web applications. By the end of this lab, students should have their HelloWorld app hosting photos.

\subsection*{Lab format}
Like previous labs, this lab primarily guides students through the process of adding photos, with comprehension questions placed throughout.

\subsection*{Required materials}
Students will need:
\begin{itemize*}
\item Their completed HelloWorld app from the end of Lab 3
\item A laptop with an internet connection
\item Photos from \href{http://interfacelift.com}{interfacelift} in \verb!public/img/interfacelift!
\end{itemize*}


\subsection*{Grading rubric}
\begin{tabular}{p{5.5in} r}
Task 1 is worth \textbf{5} points. & $1 \times 5 = 5$ \\
Tasks 2-4 are worth \textbf{10} points each. & $3 \times 10 = 30$ \\
Questions 1-5 are worth \textbf{5} points each. & $5 \times 5 = 25$ \\
Question 6 is worth \textbf{10} points. & $1 \times 10 = 10$ \\ \hline
& \textbf{70} points
\end{tabular}

\subsection*{Due date}
The lab is due \textcolor{red}{\textbf{\labduedate}}.

\input{../common/turnin}

\task{5}{Update the Model}

As in all new data entities, we first need to modify the model to provide information about the Photo type. Open \verb!models.js! and add:

\begin{minted}{javascript}
var PhotoSchema = new mongoose.Schema({
    path : String // src
  , description : String // alt
  , date : Date // timestamp
});

var Photo = mongoose.model('Photo', PhotoSchema);

Photo.count(function(err, c) {
  if (c == 0) {
    var FOLDER = 'public/img/interfacelift';
    fs.readdir(FOLDER, function(err, files) {
      for (var i in files) {
        var file = files[i];
        var photo = new Photo();
        photo.path = FOLDER.replace(FOLDER.split('/')[0], '') + '/' + file;
        photo.description = file.split('.')[0];
        photo.date = new Date();
        photo.save();
      }
    });
  }
});

exports.Photo = Photo;
\end{minted}

\question{5} When we store a Photo, what is stored in the database? What is stored on disk? Why do we make this tradeoff?

\question{5} Explain, in your own words, what the block beginning \verb!Photo.count...! does.

\task{10}{Adding Routes}

Now that our database understands photos, we need to expose an interface to users of our website to view those photos. Add to \verb!app.js!:

\begin{minted}{javascript}
routes.photos = require('./routes/photos.js');

app.get('/photos/:page', routes.photos.all);
\end{minted}

Now, open \verb!routes/photos.js! and add the following route:

\begin{minted}{javascript}
var Photo = require('../models').Photo;

exports.all = function(req, res) {
  var page = parseInt(req.params.page) || 0; // :page or all (first page)
  var options;
  if (page == 0) { // first page is a special case
    options = {limit: 2};
  } else {
    options = {skip: page - 1, limit: 3};
  }
  Photo.find({}, ['path', 'description'], options, function(err, photos) {
    var n = photos.length;
    var context;
    if (n == 0) {
      context = {'left': null, 'center': null, 'right': null};
    } else if (n == 1) {
      context = {'left': null, 'center': photos[0], 'right': null};
    } else if (n == 2) {
      if (page == 0) { // first page is a special case
        context = {'left': null, 'center': photos[0], 'right': photos[1]};
      } else {
        context = {'left': photos[0], 'center': photos[1], 'right': null};
      }
    } else if (n == 3) {
      context = {'left': photos[0], 'center': photos[1], 'right': photos[2]};
    }
    context.page = page;
    context.title = 'Photos';
    context.stylesheet = 'photos.css';
    res.render('photos', context);
  });
};
\end{minted}

\question{5} Can you think of a way to shorten the large \verb!if! block in the middle of this route?

\question{5} What will the value of the variable \verb!page! be if a user accesses the route \verb!/photos/all!? \verb!/photos/2!? \verb!/photos/null!?

\task{10}{Adding a View}

You'll notice that the end of the route from the previous task attempts to render a nonexistent page. Let's go ahead and create that page now. Open the file \verb!views/photos.jade! and insert:

\begin{minted}{jade}
if center
  .row
    .span2
      if left
        a(href='/photos/' + (page - 1))
          img(src=left.path, alt=left.description)
      else
        &nbsp;
    .span6.offset1
      a(href='/photo/' + center.description)
        img(src=center.path, alt=center.description)
    .span2.offset1
      if right
        a(href='/photos/' + (page + 1))
          img(src=right.path, alt=right.description)
      else
        &nbsp;
  br
div.alert.alert-info="All photos licensed by InterfaceLIFT.com for personal use only."
\end{minted}

\question{5} Does this view correctly handle edge cases for values of the \verb!page! variable? If not, how does it break?

\subsection*{Running the App}

As always, run the app (and check new functionality) by running:

\verb!node app.js!

Then access the app at \href{http://localhost:3000/photos}{http://localhost:3000/photos}.

\task{10}{Refactoring}

If you identified any issues in the process of answering the questions above, fix them in the app. Be sure to \textbf{commit your changes separately} from any code from other tasks.

\question{10} What did you change? Why?

\input{../common/turnin}

\subsection*{Revision History}
\begin{itemize*}
\item April 14, 2012: Lab written by Samad Jawaid
\item April 16, 2012: Lab questions and instructions filled out by Tim Ekl
\end{itemize*}

\end{document}
