%%%
% CSSE lab template
% Written March 28, 2011 by Tim Ekl
%
% This template is part of a template system; you should be generating a lab
% using the newlab.sh file. Once you have generated the lab, feel free to
% remove this comment.
%
% This lab has five TODO items that need to be completed manually after
% generating the lab from template. Suggestions are provided with each TODO.
%
% For more info and examples of labs built from this template, see:
% http://github.com/CSSE376/Labs (note you must be a 376 TA to access)
%%%

\documentclass{article}

\newcommand{\labduedate}{at the end of Week 2}

\input{../common/header}

\pagestyle{fancy}
\headheight 24pt
\begin{document}

\chead{\textcolor{Gray}{CSSE491 -- Scalable Computing Lab Assignment}}
\headsep = 24pt

\begin{center}
{ \large
\textbf{Lab \labnumber: \longproductname} \\
\textbf{Modifying Data}
}
\end{center}

\subsection*{Objective}
This lab builds on lab 1 to introduce students to the process of modifying data in a Node.js application using REST principles.

\subsection*{Lab format}
As with lab 1, this lab is almost entirely guided; it walks students through the process of adding a route and corresponding view to the existing HelloWorld Node.js application.

\subsection*{Required materials}
Students need a laptop, an Internet connection, and the HelloWorld app created in lab 1.

\subsection*{Grading rubric}
\begin{tabular}{p{5.5in} r}
Tasks 1 and 2 are worth \textbf{10} points each & $2 \times 10 = 20$ \\ \hline
& \textbf{20} points total
\end{tabular}

\subsection*{Due date}
The lab is due \textcolor{red}{\textbf{\labduedate}}.

\input{../common/turnin}

\task{10}{Add a Route}

Open the file \verb!app.js!. In the Routes section, add:

\begin{minted}{javascript}
app.post('/statuses', routes.create_status)
\end{minted}

This binds the \verb!/statuses! path in your webapp to a function called \verb!create_status! in the routes definition file. Next we need to implement that function. Open the file \verb!routes/index.js! and add at the end:

\begin{minted}{javascript}
/*
 * POST create status
 */

exports.create_status = function(req, res) {
    var status = new Status();
    status.message = req.body.message;
    status.save();
    res.redirect('back');
};
\end{minted}

\task{10}{Add a view}

Now we can add statuses to our application, but we'd have to hit the \verb!/statuses! URL manually; let's make this easier on our users by changing our views to allow status creation from entirely within the webapp. Open the file \verb!views/index.jade! and add at the end:

\begin{minted}{jade}
h2 Create Status
form(method="post", action="/statuses")
  div
    label Message:
    input(name="message")
  div
    input(type="submit", value="Create status")
\end{minted}

\subsection*{Test the App}

At a shell, run the webapp with:

\begin{minted}{bash}
node app.js
\end{minted}

Check to see that you can add a status by going to \href{http://localhost:3000/}{http://localhost:3000} and using the status-creation box you see there.

\input{../common/turnin}

\subsection*{Revision History}
\begin{itemize*}
\item April 13, 2012: Lab converted to LaTeX by Tim Ekl
\item March 13, 2012: Lab written by Samad Jawaid
\end{itemize*}

\end{document}
